---
title: "Financial Inclusion in Mexico"
author: "Esteban Castaneda"
date: "January 27, 2019"
output: 
  html_document:
    code_folding: hide
---

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(readxl)
library(dbplyr)
library(dplyr)
library(directlabels)
library(ggridges)
library(gridExtra)
library(grid)
library(treemapify)
library(viridis)
library(haven)
library(rgdal)
library(sf)
library(broom)
library(scales)

#Create Scale of colors:
ecm_colors <- c(`blue`="#719bff", `pink`="#ff6969",`red`="#ff0000" ,`orange`="#ff9f15", `yellow`="#fffb05",`green`="#5da94a",`grey`="#ebebeb")

#Function to get the colors:
ecm_cols <- function(...) {
  cols <- c(...)
  if (is.null(cols))
    return (ecm_colors)
  ecm_colors[cols]
}

#Create colors lists:
ecm_palettes <- list(`main`=ecm_cols("blue", "pink", "orange","yellow","red","grey","green"),
  `cool`=ecm_cols("blue", "pink"),
  `hot` = ecm_cols("yellow", "orange","red"),
  `mix`=ecm_cols("blue","pink","orange","yellow"),
  `drivelight`=ecm_cols("green","yellow","orange","red"),`banks`=ecm_cols("blue","red","green","yellow","orange","grey"),`reasons`=ecm_cols("orange","grey","blue","red","green","yellow"))

ecm_pal <- function(palette = "main", reverse = FALSE, ...) {
  pal <- ecm_palettes[[palette]]
  if (reverse) pal <- rev(pal)
  colorRampPalette(pal, ...)
}

scale_color_ecm <- function(palette = "main", discrete = TRUE, reverse = FALSE, ...) {
  pal <- ecm_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("ecm_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

scale_fill_ecm <- function(palette = "main", discrete = TRUE, reverse = FALSE, ...) {
  pal <- ecm_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("fill", paste0("ecm_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}


```

At a worldwide level, economies have become conscious about the relevance of financial inclusion as an enabler of development. This awareness has been recognized by several international organizations like the OECD and the UN, who consider financial inclusion national strategies a key factor to eradicate poverty, end hunger, gender equality and economic empowerment of women, promote economic growth and jobs, promote industry innovation and infrastructure, among others.

### The world's financial inclusion trend.

Since 2011, the level of financial inclusion has increased. As can be seen in the following graph, the distribution of the account ownership indicator across 126 economies has shifted from the lower to the upper range. Moreover, in all the years the distribution shows a multimodal behavior which is basically due to the type of countries included in the sample: developed and developing. 


```{r, echo=TRUE, fig.height=8, fig.width=12, message=FALSE}
#Read the World Bank Global Findex data and the GDP per capita from the World Development Indicators data: 
WB_GFdata<-read_excel(path=here('Data','FINDEXEXCEL.xlsx'),sheet = 'Data'
                    ,range=cell_rows(1:142009)
                    ,col_names = TRUE
                    ,col_types=c(rep("text",4), rep("numeric", 3)))

WB_WDdata<-read_excel(path=here('Data','WDIEXCEL.xlsx'),sheet = 'Data2'
                      ,range=cell_rows(1:265)
                      ,col_names = TRUE
                      ,col_types=c(rep("text",4), rep("numeric", 58)))

#Graph 1: Evolution of the accounts indicator.

# From Global Findex data we filter the Account (% age 15+) indicator only for countries without NA.
WB_account<-WB_GFdata %>% 
  filter(`Indicator Code`=='account.t.d', !is.na(`2011`),!is.na(`2014`),!is.na(`2017`))

WLD_2011<-WB_account$`2011`[WB_account$`Country Code`=="WLD" & WB_account$`Indicator Code`=='account.t.d']
WLD_2014<-WB_account$`2014`[WB_account$`Country Code`=="WLD" & WB_account$`Indicator Code`=='account.t.d']
WLD_2017<-WB_account$`2017`[WB_account$`Country Code`=="WLD" & WB_account$`Indicator Code`=='account.t.d']
WLD<-c(WLD_2011,WLD_2014,WLD_2017)

#The first 20 records of the dataset belong to groups of countries, so we will exclude them for the first graph. 
regions<-c('ARB','EAS','EAP','EMU','ECS','ECA','HIC','LCN','LAC','LMY','LIC','LMC','MIC','NAC','OED','SAS','SSF','SSA','UMC','WLD')

WB_account<-WB_account %>% 
  group_by(`Country Code`) %>%
  filter(!(`Country Code` %in% regions)) %>% 
  gather(`2011`:`2017`, key='year', value='account.t.d') %>%
  arrange(year, .by_group = TRUE)

#Additionally we add a flag to indicate if the country indicator is above or below the world aggregate level for each year, 
#as well as a flag to identify Mexico.
WB_account$Group<-'1. Countries below the world mean level'
WB_account$Group[WB_account$year==2011 & WB_account$account.t.d>WLD[1]]<-'2. Countries above the world mean level'
WB_account$Group[WB_account$year==2014 & WB_account$account.t.d>WLD[2]]<-'2. Countries above the world mean level'
WB_account$Group[WB_account$year==2017 & WB_account$account.t.d>WLD[3]]<-'2. Countries above the world mean level'
WB_account$MEX<-0
WB_account$MEX[WB_account$`Country Code`=='MEX']<-1

#Make a graph to understand the evolution of the distribution for the accounts indicator. 
WB_account %>% ggplot(aes(y=year,x=account.t.d/100,fill=..x..))+
  geom_density_ridges_gradient(scale =0.9, alpha = 0.9)+
  scale_fill_ecm(palette = "drivelight", discrete = FALSE,reverse = TRUE)+
  theme_minimal()+
  labs(title = "Evolution of the distribution of account ownership indicator in 126 countries.",subtitle="Every year the account ownership at a financial institution or with a mobile-money-service provider in the world is increasing.", caption="World Bank Group: Global Findex database",y="Year",x="Average number of accounts per inhabitant",fill="Accounts")+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.subtitle =element_text(color = "grey20", size = 15, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 20, angle = 0, hjust = 0, vjust = .5, face = "bold"))



```

### Mexico's financial inclusion trend.

Mexico is one of the developing countries that is struggling with the financial inclusion issue. According to the World Bank Group, the account ownership indicator in the country increased from 2011 to 2014, just like the rest of the world's regions, but did not follow the world's tendency from 2014 to 2017. This behavior is particularly interesting because even the low income regions had shown an increases in financial inclusion.

```{r, echo=TRUE, fig.height=8, fig.width=12, message=FALSE}

WB_account<-WB_GFdata %>% 
  filter(`Indicator Code`=='account.t.d', !is.na(`2011`),!is.na(`2014`),!is.na(`2017`))

WB_GDPpc<-WB_WDdata %>% 
  filter(!is.na(`2011`),!is.na(`2014`),!is.na(`2017`))


#We will filter the information at regional levels. 
regions<-c('HIC','LIC','MIC','WLD','MEX')

WB_account<-WB_account %>% 
  group_by(`Country Code`) %>%
  filter(`Country Code` %in% regions) %>% 
  gather(`2011`:`2017`, key='year', value='account.t.d') %>%
  arrange(year, .by_group = TRUE)

WB_GDPpc<-WB_GDPpc %>% 
  group_by(`Country Code`) %>%
  filter(`Country Code` %in% regions) %>% 
  gather(`1960`:`2017`, key='year', value='GDP per capita') %>%
  arrange(year, .by_group = TRUE) %>%
  filter(year %in% c(2011,2014,2017)) %>%
  select(`Country Code`,year,`GDP per capita`)


WB_account<-inner_join(WB_account,WB_GDPpc, by=c('Country Code', 'year'))
names(WB_account)[1]<-"Region Name"
names(WB_account)[2]<-"Region Code"
WB_account<-WB_account %>% 
  group_by(`Region Code`)


region_colors<-c("High income" = ecm_pal('hot')(3)[1],"Middle income" = ecm_pal('hot')(3)[2],"Low income" = ecm_pal('hot')(3)[3],"World" = ecm_colors[1], "Mexico" = ecm_colors[6])
names(region_colors)<-c("High income","Middle income","Low income","World","Mexico")

#Make a graph to compare Mexico with groups of countries by income. 
WB_account %>% ggplot(aes(x=year,y=account.t.d/100, group=`Region Name`))+
  geom_line(aes(color=`Region Name`,size=1.5), show.legend = FALSE)+
  geom_dl(aes(label = `Region Name`), method=list(dl.trans(x = x + 0.5), "last.points", cex = 0.8))+
  theme_minimal()+
  geom_point(aes(size=2,color=`Region Name`),alpha=1,show.legend = FALSE)+
  scale_colour_manual(values=region_colors, guide=FALSE)+
  labs(subtitle = "Account ownership indicator and GDP per capita by Income Region and year.",title="While most countries have improved, Mexico has not.", caption="World Bank Group: Global Findex and World Development Indicators datasets.",x="Year",y="Average number of accounts per inhabitant")+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.subtitle =element_text(color = "grey20", size = 15, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 20, angle = 0, hjust = 0, vjust = .5, face = "bold"))




```

### What's the status of financial service adoption in Mexico?

As of June 2018, the financial service with the highest adoption rate is the deposit account, whereas the insurance is the one with the lowest adoption rate. Moreover, there is a gender gap in the country, which is particularly higher in the retirement account services, but this is not as critical as the one related to the community size. To properly attend the financial inclusion issue is important to understand why the population is not acquiring the services.



```{r, echo=TRUE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE}
ENIF18_df1<-read_excel(path=here('Data','tmodulo.xlsx'),sheet = 'tmodulo'
                       ,range=cell_rows(1:12447)
                       ,col_names = TRUE
                       ,col_types=c(rep("text",221), rep("numeric", 1)))

ENIF18_df2<-read_excel(path=here('Data','tmodulo2.xlsx'),sheet = 'tmodulo2'
                       ,range=cell_rows(1:12447)
                       ,col_names = TRUE
                       ,col_types=c(rep("text",148), rep("numeric", 1)))

# Preparing the data.
#From the table ENIF18_df1 we will get the indicators of account ownership and credit holding, whereas from 
# table ENIF18_df2 we will get the insurance and retirement funds holdings. 

ENIF18_df1$TLOC[ENIF18_df1$TLOC==2]<-1
ENIF18_df1$TLOC[ENIF18_df1$TLOC==3]<-2
ENIF18_df1$TLOC[ENIF18_df1$TLOC==4]<-2
ENIF18_df2$TLOC[ENIF18_df2$TLOC==2]<-1
ENIF18_df2$TLOC[ENIF18_df2$TLOC==3]<-2
ENIF18_df2$TLOC[ENIF18_df2$TLOC==4]<-2


MEX_Inhabitants<-sum(ENIF18_df1$FAC_PER)
MEX_Inhabitants_d<-ENIF18_df1 %>% select('SEXO', 'TLOC', 'FAC_PER') %>%
  group_by(.dots=c('SEXO', 'TLOC')) %>%
  summarise(Inhabitants=sum(FAC_PER))

MEX_accounts<-ENIF18_df1 %>% 
  filter(P5_4=='1' | P5_5=='1') %>%
  select('SEXO', 'TLOC', 'FAC_PER') %>%
  group_by(.dots=c('SEXO', 'TLOC')) %>%
  summarise(account=sum(FAC_PER))

MEX_credits<-ENIF18_df1 %>% 
  filter(P6_3=='1' | P6_4=='1') %>%
  select('SEXO', 'TLOC', 'FAC_PER') %>%
  group_by(.dots=c('SEXO', 'TLOC')) %>%
  summarise(credits=sum(FAC_PER))

MEX_insurance<-ENIF18_df2 %>% 
  filter(P8_1=='1' | P8_2=='1') %>%
  select('SEXO', 'TLOC', 'FAC_PER') %>%
  group_by(.dots=c('SEXO', 'TLOC')) %>%
  summarise(insurance=sum(FAC_PER))

MEX_retirement<-ENIF18_df2 %>% 
  filter(P9_1=='1') %>%
  select('SEXO', 'TLOC', 'FAC_PER') %>%
  group_by(.dots=c('SEXO', 'TLOC')) %>%
  summarise(retirement=sum(FAC_PER))

MEX_indicators<-MEX_Inhabitants_d %>% 
  inner_join(MEX_accounts, by=c('SEXO','TLOC')) %>%
  inner_join(MEX_credits, by=c('SEXO','TLOC')) %>%
  inner_join(MEX_insurance, by=c('SEXO','TLOC')) %>%
  inner_join(MEX_retirement, by=c('SEXO','TLOC'))

MEX_indicators_SEXO<-MEX_indicators %>%
  select(-'TLOC') %>%
  group_by(.dots=c('SEXO')) %>%
  summarise_all(funs(sum))
  
MEX_indicators_TLOC<-MEX_indicators %>%
  group_by(.dots=c('TLOC')) %>%
  select(-'SEXO') %>%
  group_by(.dots=c('TLOC')) %>%
  summarise_all(funs(sum))


MEX_indicators<-MEX_indicators %>% 
  mutate(accounts_p=100*account/Inhabitants) %>%
  mutate(credits_p=100*credits/Inhabitants) %>%
  mutate(insurance_p=100*insurance/Inhabitants) %>%
  mutate(retirement_p=100*retirement/Inhabitants) %>%
  select('SEXO', 'TLOC', 'accounts_p','credits_p','insurance_p','retirement_p')

MEX_indicators_SEXO<-MEX_indicators_SEXO %>% 
  mutate(accounts_p=100*account/Inhabitants) %>%
  mutate(credits_p=100*credits/Inhabitants) %>%
  mutate(insurance_p=100*insurance/Inhabitants) %>%
  mutate(retirement_p=100*retirement/Inhabitants) %>%
  select('SEXO', 'accounts_p','credits_p','insurance_p','retirement_p')

MEX_indicators_TLOC<-MEX_indicators_TLOC %>% 
  mutate(accounts_p=100*account/Inhabitants) %>%
  mutate(credits_p=100*credits/Inhabitants) %>%
  mutate(insurance_p=100*insurance/Inhabitants) %>%
  mutate(retirement_p=100*retirement/Inhabitants) %>%
  select('TLOC', 'accounts_p','credits_p','insurance_p','retirement_p')

names(MEX_indicators)<-c('SEXO', 'TLOC', 'Deposit account','Credit','Insurance','Retirement account')

names(MEX_indicators_SEXO)<-c('SEXO', 'Deposit account','Credit','Insurance','Retirement account')

names(MEX_indicators_TLOC)<-c('TLOC', 'Deposit account','Credit','Insurance','Retirement account')

MEX_indicators<-MEX_indicators %>% 
  group_by(.dots=c('SEXO', 'TLOC')) %>%
  gather(`Deposit account`:`Retirement account`, key='Financial Service', value='Indicator')

MEX_indicators_SEXO<-MEX_indicators_SEXO %>% 
  group_by(.dots=c('SEXO')) %>%
  gather(`Deposit account`:`Retirement account`, key='Financial Service', value='Indicator')

MEX_indicators_TLOC<-MEX_indicators_TLOC %>% 
  group_by(.dots=c('TLOC')) %>%
  gather(`Deposit account`:`Retirement account`, key='Financial Service', value='Indicator')


MEX_indicators$SEXO[MEX_indicators$SEXO=='1']<-'Male'
MEX_indicators$SEXO[MEX_indicators$SEXO=='2']<-'Female'
MEX_indicators$TLOC[MEX_indicators$TLOC=='1']<-'15,000 or more'
MEX_indicators$TLOC[MEX_indicators$TLOC=='2']<-'14,999 or less'

MEX_indicators_SEXO$SEXO[MEX_indicators_SEXO$SEXO=='1']<-'Male'
MEX_indicators_SEXO$SEXO[MEX_indicators_SEXO$SEXO=='2']<-'Female'
MEX_indicators_TLOC$TLOC[MEX_indicators_TLOC$TLOC=='1']<-'15,000 or more inhabitants'
MEX_indicators_TLOC$TLOC[MEX_indicators_TLOC$TLOC=='2']<-'14,999 or less inhabitants'

names(MEX_indicators)<-c('Gender', 'Community Size', 'Financial Service', 'Indicator')

names(MEX_indicators_SEXO)<-c('Group', 'Financial Service', 'Indicator')
names(MEX_indicators_TLOC)<-c('Group', 'Financial Service', 'Indicator')

MEX_indicators_2<-merge(MEX_indicators_SEXO,MEX_indicators_TLOC, all=TRUE)
MEX_indicators_2$`Gap`<-"Community Size"
MEX_indicators_2$`Gap`[MEX_indicators_2$Group=='Male'|MEX_indicators_2$Group=='Female']<-"Gender"


MEX_indicators_2 %>% ggplot(aes(y=Indicator,x=`Financial Service`,fill=Group))+
  facet_wrap(Gap~.,scales = 'free')+
  theme_minimal()+
  scale_y_continuous(expand = c(0,0),limits = c(0,70))+
  geom_bar(stat='Identity',position=position_dodge())+
  scale_fill_ecm(palette = 'mix',reverse = TRUE)+
  geom_text(aes(label=round(Indicator,digits=2)),position=position_dodge(0.9), vjust=-1)+
  theme(legend.position="top",legend.title = element_blank(), legend.spacing.x = unit(1,'cm'))+
  labs(subtitle = "The critical gaps for the financial services adoption in the country depend more on the community size than in the gender.",title="In Mexico the gender is not the only gap for financial services adoption.", caption="INEGI: National Survery of Financial Inclusion 2018.",x="Financial service",y="Percentage of population (between 18 and 70 years) with a financial service account")+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.subtitle =element_text(color = "grey20", size = 15, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))




```

The gap in the financial services adoption is also very clear at State level. When comparing the States, Nuevo León and Mexico City are the ones with high number of accounts and branches per 10,000 inhabitants, whereas Chiapas and Oaxaca are the ones with the lowest numbers. Additionally, there's a clear difference between the North and South regions of the country.    

```{r, echo=TRUE, message=FALSE, warning=FALSE , fig.height=9, fig.width=14}
CONAPO_df1<-read_excel(path=here('Data','POB_CONAPO.xlsx'),sheet = 'Poblacion18_70'
                     ,range=cell_rows(1:33)
                     ,col_names = TRUE
                     ,col_types=c(rep("text",3), rep("numeric", 4)))

names(CONAPO_df1)[1]<-'id'

MEX_map_state<-readOGR(here('Data','MAPSMX_STATE'), layer="areas_geoestadisticas_estatales", verbose = FALSE)
MEX_map_state_df <- fortify(MEX_map_state, region="CVE_ENT")

CNBV_df1<-read_excel(path=here('Data','BM_Operativa_1118.xlsx'),sheet = 'Sucursales'
                     ,range=cell_rows(1:618)
                     ,col_names = TRUE
                     ,col_types=c(rep("text",4), rep("numeric", 1)))

top_banks<-c("BBVA Bancomer",	"Banorte",	"Banamex","Banco Azteca","Santander")

Branches_bank_state<-CNBV_df1
Branches_bank_state$Group<-Branches_bank_state$nombre_publicacion
Branches_bank_state$Group[!(Branches_bank_state$nombre_publicacion %in% top_banks)]<-'Others'


CNBV_df2<-read_excel(path=here('Data','BM_Operativa_1118.xlsx'),sheet = 'Cuentas'
                     ,range=cell_rows(1:651)
                     ,col_names = TRUE
                     ,col_types=c(rep("text",4), rep("numeric", 1)))

Accounts_bank_state<-CNBV_df2
Accounts_bank_state$Group<-Accounts_bank_state$nombre_publicacion
Accounts_bank_state$Group[!(Accounts_bank_state$nombre_publicacion %in% top_banks)]<-'Others'

MEX_Branches_State<-Branches_bank_state %>%
  select('cve_inegi', 'Num_Sucursales') %>%
  group_by(.dots=c('cve_inegi')) %>%
  summarise(`Branches`=sum(Num_Sucursales)) %>%
  gather(`Branches`, key='Variable', value='Branches')

names(MEX_Branches_State)[1]<-'id'

MEX_Accounts_State<-Accounts_bank_state %>%
  select('cve_inegi', 'Num_Cuentas') %>%
  group_by(.dots=c('cve_inegi')) %>%
  summarise(`Accounts`=sum(Num_Cuentas)) %>%
  gather(`Accounts`, key='Variable', value='Accounts')

names(MEX_Accounts_State)[1]<-'id'

MEX_Pop_Acc_Branch<-CONAPO_df1 %>%
  select('id','dl_estado_short','POB_1118') %>%
  group_by(.dots=c('id')) %>%
  inner_join(MEX_Accounts_State,by=c('id')) %>%
  inner_join(MEX_Branches_State,by=c('id')) %>%
  mutate(Branches_p=round(10000*Branches/POB_1118,2)) %>%
  mutate(Accounts_p=round(10000*Accounts/POB_1118,2)) %>%
  select('id','Branches_p', 'Accounts_p')

names(MEX_Pop_Acc_Branch)<-c('id', 'Branches per 10,000 inhabitants','Accounts per 10,000 inhabitants')

Map_MEX_Pop_Acc_Branch <- inner_join(MEX_map_state_df, MEX_Pop_Acc_Branch, by="id")
Map_Labels<-Map_MEX_Pop_Acc_Branch %>%
  select('id','long','lat') %>%
  group_by(.dots=c('id')) %>%
  summarise_all(funs(mean))
  
Map_Labels$Labels[Map_Labels$id=='19']<-'NL'
Map_Labels$Labels[Map_Labels$id=='09']<-'MC'

Map_MEX_Pop_Acc_Branch %>% ggplot() +
  geom_polygon(aes(x=long, y=lat, group=group, fill=`Accounts per 10,000 inhabitants`),color='white')+
  geom_text(data=Map_Labels,aes(x=long, y=lat, label=Labels))+
  theme_minimal()+
  theme(legend.position = 'bottom', legend.key.width = unit(1,'cm'))+
  scale_fill_ecm(palette = 'cool',discrete = FALSE, reverse = TRUE,labels=comma)+
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_blank())+
  labs(x=NULL, y=NULL, title="Mexico City and Nuevo Leon are the states with more accounts per 10,000 inhabitants in Mexico" ,subtitle="The South region is the most backward of the country.",caption="CNBV: Balance sheet historical series.")+
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),legend.position = "bottom",plot.subtitle =element_text(color = "grey20", size = 13, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))


```

### Why are the Mexicans not acquiring financial services?

According to the 2018 National Survey of Financial Inclusion, based on a 14,500 household sample all over the country, the main reasons for not acquiring a financial service can be grouped in 5 categories: Lack of interest, Unattractive offer, Distrust in the financial institutions, Non affordability, Ignorance regarding the financial service. The first four categories are directly related with the quality and cost of the service offer, whereas the last one is related to the financial education.

```{r, echo=TRUE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE}
#Regroup the variables:
ENIF18_df1$P5_7_2[ENIF18_df1$P5_7==5|ENIF18_df1$P5_7==6]<-'1'
ENIF18_df1$P5_7_2[ENIF18_df1$P5_7==2]<-'2'
ENIF18_df1$P5_7_2[ENIF18_df1$P5_7==8]<-'3'
ENIF18_df1$P5_7_2[ENIF18_df1$P5_7==4|ENIF18_df1$P5_7==7]<-'4'
ENIF18_df1$P5_7_2[ENIF18_df1$P5_7==3]<-'5'
ENIF18_df1$P5_7_2[ENIF18_df1$P5_7==1|ENIF18_df1$P5_7==9]<-'6'

ENIF18_df1$P6_6_2[ENIF18_df1$P6_6==6|ENIF18_df1$P6_6==7]<-'1'
ENIF18_df1$P6_6_2[ENIF18_df1$P6_6==5]<-'2'
ENIF18_df1$P6_6_2[ENIF18_df1$P6_6==1]<-'4'
ENIF18_df1$P6_6_2[ENIF18_df1$P6_6==4]<-'5'
ENIF18_df1$P6_6_2[ENIF18_df1$P6_6==2|ENIF18_df1$P6_6==3|ENIF18_df1$P6_6==8]<-'6'

ENIF18_df2$P8_4_2[ENIF18_df2$P8_4==7]<-'1'
ENIF18_df2$P8_4_2[ENIF18_df2$P8_4==6]<-'2'
ENIF18_df2$P8_4_2[ENIF18_df2$P8_4==5]<-'3'
ENIF18_df2$P8_4_2[ENIF18_df2$P8_4==4]<-'4'
ENIF18_df2$P8_4_2[ENIF18_df2$P8_4==2]<-'5'
ENIF18_df2$P8_4_2[ENIF18_df2$P8_4==1|ENIF18_df2$P8_4==3|ENIF18_df2$P8_4==8]<-'6'

ENIF18_df2$P9_2_2[ENIF18_df2$P9_2==5]<-'1'
ENIF18_df2$P9_2_2[ENIF18_df2$P9_2==2|ENIF18_df2$P9_2==4]<-'3'
ENIF18_df2$P9_2_2[ENIF18_df2$P9_2==1|ENIF18_df2$P9_2==3]<-'4'
ENIF18_df2$P9_2_2[ENIF18_df2$P9_2==6]<-'5'
ENIF18_df2$P9_2_2[ENIF18_df2$P9_2==7|ENIF18_df2$P9_2==8]<-'6'

#Generate the tables 
MEX_accounts<-ENIF18_df1 %>% 
  filter(is.na(P5_7_2)==FALSE) %>%
  select('P5_7_2', 'FAC_PER') %>%
  group_by(.dots=c('P5_7_2')) %>%
  summarise(`Deposit account`=sum(FAC_PER))

MEX_credits<-ENIF18_df1 %>% 
  filter(is.na(P6_6_2)==FALSE) %>%
  select('P6_6_2', 'FAC_PER') %>%
  group_by(.dots=c('P6_6_2')) %>%
  summarise(`Credit`=sum(FAC_PER))

MEX_insurance<-ENIF18_df2 %>% 
  filter(is.na(P8_4_2)==FALSE) %>%
  select('P8_4_2', 'FAC_PER') %>%
  group_by(.dots=c('P8_4_2')) %>%
  summarise(`Insurance`=sum(FAC_PER))

MEX_retirement<-ENIF18_df2 %>% 
  filter(is.na(P9_2_2)==FALSE) %>%
  select('P9_2_2', 'FAC_PER') %>%
  group_by(.dots=c('P9_2_2')) %>%
  summarise(`Retirement account`=sum(FAC_PER))

names(MEX_accounts)[1]<-'Reasons'
names(MEX_credits)[1]<-'Reasons'
names(MEX_insurance)[1]<-'Reasons'
names(MEX_retirement)[1]<-'Reasons'

MEX_indicators<-MEX_accounts %>% 
  left_join(MEX_credits, by=c('Reasons')) %>%
  left_join(MEX_insurance, by=c('Reasons')) %>%
  left_join(MEX_retirement, by=c('Reasons'))

MEX_indicators$Reasons[MEX_indicators$Reasons=='1']<-'Lack of interest'
MEX_indicators$Reasons[MEX_indicators$Reasons=='2']<-'Unattractive offer'
MEX_indicators$Reasons[MEX_indicators$Reasons=='3']<-'Ignorance'
MEX_indicators$Reasons[MEX_indicators$Reasons=='4']<-'Non affordable'
MEX_indicators$Reasons[MEX_indicators$Reasons=='5']<-'Institutional Distrust'
MEX_indicators$Reasons[MEX_indicators$Reasons=='6']<-'Others'

MEX_indicators2<-MEX_indicators

for (i in 2:5){
  MEX_indicators2[,i]<-MEX_indicators2[,i] %>% replace(is.na(MEX_indicators2[,i]),0)
  MEX_indicators2[,i]<-round(100*MEX_indicators2[,i]/sum(MEX_indicators2[,i]),2)
  }

MEX_indicators<-MEX_indicators %>% 
  group_by(Reasons) %>%
  gather(`Deposit account`:`Retirement account`, key='Financial Service', value='Respondents') %>%
  arrange(`Financial Service`, .by_group = TRUE)

MEX_indicators2<-MEX_indicators2 %>% 
  group_by(Reasons) %>%
  gather(`Deposit account`:`Retirement account`, key='Financial Service', value='Percentage') %>%
  arrange(`Financial Service`, .by_group = TRUE)

MEX_indicators<-MEX_indicators %>% 
  left_join(MEX_indicators2, by=c('Reasons','Financial Service'))
  


MEX_indicators %>% ggplot(aes(area=Respondents, fill=Reasons, subgroup=Reasons))+
  facet_wrap(~`Financial Service`)+
  geom_treemap()+
  geom_treemap_subgroup_border(color='grey100')+
  geom_treemap_text(aes(label=paste(Percentage,"%")), color="black")+
  scale_x_continuous(expand = c(0, 0), position='top') +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_ecm(palette = 'reasons')+
  theme(legend.position="bottom")+
  labs(subtitle = "Main reasons for not acquire a financial service.",title="Affordability and Lack of Interest are the main reasons for not acquiring a financial service.", caption="INEGI: National Survery of Financial Inclusion 2018.",x="Percentage of respondents without the financial service.")+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 0, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.subtitle =element_text(color = "grey20", size = 15, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))

```

### If the financial inclusion in the country is stuck, is the banking industry in Mexico growing?

Although the World Bank Group data indicate that the financial inclusion in Mexico is trapped, the amount of deposits and credit lines in the country had increased in the last years, whereas the credit portfolio quality had decreased. This indicates that the banks are collecting more money and installing more credit lines with better quality. In other words, the financial inclusion level in Mexico is not growing, but the amount of deposits and credits are.   

```{r, echo=TRUE, fig.height=8, fig.width=14, message=FALSE, warning=FALSE}
#Read the captation and credit data from the CNBV:
CNBV_df1<-read_excel(path=here('Data','SH_BM_1118_1.xlsx'),sheet = 'Table_1'
                       ,range=cell_rows(1:217)
                       ,col_names = TRUE
                       ,col_types=c(rep("date",1), rep("numeric", 4)))

CNBV_df1$Year<-format(CNBV_df1$Date,"%Y")

CNBV_Average<-CNBV_df1 %>% 
  select('Year', 'Deposits','Credits','IMOR','USD') %>%
  group_by(.dots=c('Year')) %>%
  summarise_all(funs(mean))

CNBV_Average$`Deposits (USD)`<-CNBV_Average$Deposits/CNBV_Average$USD
CNBV_Average$`Credits (USD)`<-CNBV_Average$Credits/CNBV_Average$USD

CNBV_Average_Balance<-CNBV_Average %>% 
  select('Year', 'Deposits (USD)','Credits (USD)') %>%
  group_by(Year) %>%
  gather(`Deposits (USD)`:`Credits (USD)`, key='Variable', value='Amount')

CNBV_Average_Balance<-CNBV_Average_Balance %>% 
  group_by(Variable) %>%
  dplyr::mutate(last = dplyr::last(Amount))

CNBV_Average_Balance$Variable[CNBV_Average_Balance$Variable=='Credits (USD)']<-'Credits'
CNBV_Average_Balance$Variable[CNBV_Average_Balance$Variable=='Deposits (USD)']<-'Deposits'

CNBV_Average_Indicators<-CNBV_Average %>% 
  select('Year', 'IMOR') %>%
  group_by(Year) %>%
  gather(IMOR, key='Variable', value='Indicator') %>%
  arrange(Variable, .by_group = TRUE)

CNBV_Average_Indicators<-CNBV_Average_Indicators %>% 
  group_by(Variable) %>%
  dplyr::mutate(last = dplyr::last(Indicator))

CNBV_Average_Indicators$Variable[CNBV_Average_Indicators$Variable=='IMOR']<-'Credit Default Rate'

p5<-CNBV_Average_Balance %>% ggplot(aes(x = Year, y = Amount/1000,group=Variable)) + 
  geom_line(aes(color = Variable), alpha = 1, size=2)+
  geom_dl(aes(label = round(last/1000,0)), method=list(dl.trans(y=y+0.2,x = x-0.25), "last.points", cex = 0.8))+
  scale_color_manual(values = c("#719bff", "#f5f856")) +
  scale_fill_manual(values = c("#719bff", "#f5f856"))+
  theme_minimal()+
  theme(legend.position="bottom")+
  labs(subtitle = "Assets and Liabilities Balance.",y="Billions of US dollars",caption="CNBV: Balance sheet historical series.")+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.subtitle =element_text(color = "grey20", size = 13, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))

p6<-CNBV_Average_Indicators %>% ggplot(aes(x = Year, y = Indicator,group=Variable)) + 
  geom_line(aes(color=Variable),alpha = 1, size=2)+
  geom_dl(aes(label = round(last,1)), method=list(dl.trans(y=y+0.3, x = x-0.25 ), "last.points", cex = 0.8))+
  scale_color_manual(values = c("#ff6969")) +
  scale_fill_manual(values = c("#ff6969"))+
  theme_minimal()+
  theme(legend.position="bottom")+
  labs(subtitle = "Credit risk of the overall portfolio.", caption="CNBV: Balance sheet historical series.",y="Percentage (%)")+
  theme(axis.text.x = element_text(color = "grey20", size = 10, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 12, angle = 0, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
        plot.subtitle =element_text(color = "grey20", size = 13, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))

grid.arrange(p5, p6,ncol = 2, nrow = 1, top=textGrob("The Mexican banking industry is growing and the credit risk is improving.",gp=gpar(fontsize=20,fontface='bold'),x=0,hjust = 0))

  

```

Moreover, more than 70% of the deposits are hold by five banks, whereas the remaining is hold by more than 40 institutions, which indicates that the industry follows an oligopoly structure. Besides, these five banks hold only 52% of the branches in the country, which might be because of the geographical distribution of the customers. 


```{r, echo=TRUE, message=FALSE, warning=FALSE,fig.height=8, fig.width=14}
#Branches vs Deposits:
CNBV_df2<-read_excel(path=here('Data','BM_Operativa_1118.xlsx'),sheet = 'Sucursales'
                       ,range=cell_rows(1:618)
                       ,col_names = TRUE
                       ,col_types=c(rep("text",4), rep("numeric", 1)))

CNBV_df3<-read_excel(path=here('Data','BM_Operativa_1118.xlsx'),sheet = 'Captacion'
                     ,range=cell_rows(1:51)
                     ,col_names = TRUE
                     ,col_types=c(rep("text",1), rep("numeric", 1)))

#Deposits and branchs table 
top_banks<-c("BBVA Bancomer",	"Banorte",	"Banamex",	"Santander",	"HSBC",	"Scotiabank",	"Inbursa",	"Banco del Bajío",	"Banco Azteca",	"Banregio")
top_banks<-c("BBVA Bancomer",	"Banorte",	"Banamex",	"Santander",	"HSBC")

Deps_bank<-CNBV_df3
Deps_bank$Group<-Deps_bank$Bank
Deps_bank$Group[!(Deps_bank$Bank %in% top_banks)]<-'Others'

Branchs_bank<-CNBV_df2
Branchs_bank$Group<-Branchs_bank$nombre_publicacion
Branchs_bank$Group[!(Branchs_bank$nombre_publicacion %in% top_banks)]<-'Others'

Total_deposits<-sum(Deps_bank$Deposits)

MEX_Deps_Bank<-Deps_bank %>% 
  select('Group', 'Deposits') %>%
  group_by(.dots=c('Group')) %>%
  summarise(`Deposits`=sum(Deposits)) %>%
  mutate(Deposits_p=round(round(100*Deposits/Total_deposits,1),0)) %>%
  arrange(desc(Deposits)) %>%
  group_by()

MEX_Deps_Bank_2<-MEX_Deps_Bank %>%
  select('Group','Deposits_p')%>%
  gather(Deposits_p, value, -Group) %>%
  spread(Group,value) %>%
  select(-c('Deposits_p')) %>%
  select(c(top_banks,'Others'))

Total_branches<-sum(Branchs_bank$Num_Sucursales)

MEX_Branchs_Bank<-Branchs_bank %>%
  select('Group', 'Num_Sucursales') %>%
  group_by(.dots=c('Group')) %>%
  summarise(`Branches`=sum(Num_Sucursales)) %>%
  mutate(Branches_p=round(100*Branches/Total_branches,0)) %>%
  arrange(desc(Branches)) %>%
  group_by()

MEX_Branchs_Bank_2<-MEX_Branchs_Bank %>%
  select('Group','Branches_p')%>%
  gather(Branches_p, value, -Group) %>%
  spread(Group,value) %>%
  select(-c('Branches_p')) %>%
  select(c(top_banks,'Others'))

nrows <- 10
aux <- expand.grid(y = 1:nrows, x = 1:nrows)
aux$Bank<- factor(rep(names(MEX_Deps_Bank_2), MEX_Deps_Bank_2))
aux$Indicator<-'Received Deposits ($)'
aux2<- expand.grid(y = 1:nrows, x = 1:nrows)
aux2$Bank<- factor(rep(names(MEX_Branchs_Bank_2), MEX_Branchs_Bank_2))
aux2$Indicator<-'Number of Branches'

aux<-rbind(aux,aux2)

aux %>% ggplot(aes(x = x, y = y, fill = Bank)) +
  facet_wrap(~Indicator)+
  geom_tile(color = "black", size = 0.5)+
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0), trans = 'reverse')+
  scale_fill_manual(values=c('Others'=ecm_pal(palette = 'banks')(6)[6],"BBVA Bancomer"=ecm_pal(palette = 'banks')(6)[1],	"Banorte"=ecm_pal(palette = 'banks')(6)[2],	"Banamex"=ecm_pal(palette = 'cool')(6)[3],"Santander"=ecm_pal(palette = 'banks')(6)[4],"HSBC"=ecm_pal(palette = 'banks')(6)[5]))+
  labs(title="Five banks hold more than 70% of the deposits.", subtitle="These same banks hold 52% of the branches in the country.", caption="CNBV: Balance sheet historical series.")+
  theme_minimal()+
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),legend.position = "bottom",plot.subtitle =element_text(color = "grey20", size = 13, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))


```

When analyzing the branches market distribution at State level, we found that there's a high concentration, BBVA, Banamex, Banorte, Banco Azteca and Santander hold at least 50% of the branches in each State.This indicates that the growing of the financial inclusion trap might be associated to an oligopoly at regional level.

```{r,echo=TRUE, message=FALSE, warning=FALSE,fig.height=8, fig.width=14}
CNBV_df2<-read_excel(path=here('Data','BM_Operativa_1118.xlsx'),sheet = 'Sucursales'
                     ,range=cell_rows(1:618)
                     ,col_names = TRUE
                     ,col_types=c(rep("text",4), rep("numeric", 1)))

top_banks<-c("BBVA Bancomer",	"Banorte",	"Banamex","Banco Azteca","Santander")

Branchs_bank<-CNBV_df2
Branchs_bank$Group<-Branchs_bank$nombre_publicacion
Branchs_bank$Group[!(Branchs_bank$nombre_publicacion %in% top_banks)]<-'Others'


MEX_Branchs_State<-Branchs_bank %>%
  select('Group','dl_estado_short', 'Num_Sucursales') %>%
  group_by(.dots=c('Group','dl_estado_short')) %>%
  summarise(`Branches`=sum(Num_Sucursales)) %>%
  gather(`Branches`, key='Variable', value='Branches')

MEX_Branchs_State_2<-Branchs_bank %>%
  select('dl_estado_short','Num_Sucursales') %>%
  group_by(.dots=c('dl_estado_short')) %>%
  summarise(`Branches`=sum(Num_Sucursales)) %>%
  gather(`Branches`, key='Variable', value='Branches_Estado')

MEX_Branchs_State<- MEX_Branchs_State %>%
  left_join(MEX_Branchs_State_2, by=c('dl_estado_short'))

MEX_Branchs_State$`Branches Share`<-round(100*MEX_Branchs_State$Branches/MEX_Branchs_State$Branches_Estado,1)

MEX_Branchs_State %>% ggplot( aes(x = "", y=`Branches Share`,fill = Group)) +
  facet_wrap(dl_estado_short~.,ncol=8,nrow=4)+
  geom_bar(width = 1,stat='identity',color='black')+
  theme_minimal()+
  scale_fill_manual(values=c('Others'=ecm_pal(palette = 'banks')(6)[6],"BBVA Bancomer"=ecm_pal(palette = 'banks')(6)[1],	"Banorte"=ecm_pal(palette = 'banks')(6)[2],	"Banamex"=ecm_pal(palette = 'cool')(6)[3],"Santander"=ecm_pal(palette = 'banks')(6)[4],"Banco Azteca"=ecm_pal(palette = 'banks')(6)[5]))+
  theme(axis.line = element_blank(), plot.title = element_text(hjust=0.5)) + 
  coord_polar(theta = "y", start=90)+
  labs(x=NULL, y=NULL, title="The same five banks concentrate at least 50% of the branches in all the states.", subtitle="Banco Azteca and BBVA are the banks with more branches all over the country.", caption="CNBV: Balance sheet historical series.")+
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),legend.position = "bottom",plot.subtitle =element_text(color = "grey20", size = 13, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))





```

Moreover, the oligopoly structure is affecting the competition in the industry in all the country, this can be shown by analyzing the concentration index (HHI) at municipal level. According to the international standards, a market is highly concentrated if the HHI index is above 2,500 points, moderately concentrated if the index is between 1,500 and 2,500, and not concentrated if the index is below 1,500. In the case of Mexico, only 7 out of 2,458 municipalities have an HHI below 1,500, whereas 2,222 municipalities have an index above 2,500. The problem with high concentrated markets is that the lack of competition might originate high prices, low quality services, among others.        

```{r,echo=TRUE, message=FALSE, warning=FALSE , fig.height=8, fig.width=14}
MEX_map_state_df <- st_read(dsn=here('Data','MAPSMX_STATE'), layer="areas_geoestadisticas_estatales", quiet = TRUE)
MEX_map_mun_df <- st_read(dsn=here('Data','MAPSMX_MUN'), layer="areas_geoestadisticas_municipales", quiet = TRUE)

CNBV_df2<-read_excel(path=here('Data','BM_Operativa_1118.xlsx'),sheet = 'Creditos_Mun'
                     ,range=cell_rows(1:2437)
                     ,col_names = TRUE
                     ,col_types=c(rep("text",2), rep("numeric", 2)))

MEX_map_mun_cred<- MEX_map_mun_df %>%
  left_join(CNBV_df2,by=c('CVE_ENT','CVE_MUN'))
names(MEX_map_mun_cred)[4]<-'Credit Accounts'
names(MEX_map_mun_cred)[5]<-'HHI'
MEX_map_mun_cred$`Concentration Group`<-'Monopoly: HHI equal to 10,000'
MEX_map_mun_cred$`Concentration Group`[MEX_map_mun_cred$HHI<10000]<-'Very high: HHI between 5,000 and 9,999'
MEX_map_mun_cred$`Concentration Group`[MEX_map_mun_cred$HHI<5000]<-'High: HHI between 2,500 and 4,999'
MEX_map_mun_cred$`Concentration Group`[MEX_map_mun_cred$HHI<2500]<-'Moderate: HHI between 1,500 and 2,499'
MEX_map_mun_cred$`Concentration Group`[MEX_map_mun_cred$HHI<1500]<-'Low: HHI below 1,500'

ihh_groups<-c('Low: HHI below 1,500'="#5da94a",'Moderate: HHI between 1,500 and 2,499'="#fffb05",'High: HHI between 2,500 and 4,999'="#ff9f15",'Very high: HHI between 5,000 and 9,999'="#ff6969",'Monopoly: HHI equal to 10,000'="#ff0000")
ihh_groups2<-c('Low: HHI below 1,500','Moderate: HHI between 1,500 and 2,499','High: HHI between 2,500 and 4,999','Very high: HHI between 5,000 and 9,999','Monopoly: HHI equal to 10,000')

MEX_map_mun_cred %>% ggplot()+
  geom_sf(aes(fill=`Concentration Group`),color='transparent')+
  scale_fill_manual(values=ihh_groups,breaks=ihh_groups2)+
  geom_sf(data=MEX_map_state_df,color="#ebebeb",fill='transparent')+
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_line(color='white'), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_blank())+
  labs(x=NULL, y=NULL, title="The commercial credit accounts are highly concentrated.",subtitle="In 90% of the 2,458 municipalities in Mexico the concentration index (HHI) is above 2,500 points, whereas in only 7 is below 1,500.",caption="CNBV: Balance sheet historical series.")+
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),legend.position = "bottom",legend.title = element_blank(),plot.subtitle =element_text(color = "grey20", size = 13, angle = 0, hjust = 0, vjust = .5, face = "plain"),
        plot.title =element_text(color = "grey20", size = 19, angle = 0, hjust = 0, vjust = .5, face = "bold"))



```

